---
title: "HW6"
author: "Eric Morris"
date: "11/21/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelr)
library(purrr)

knitr::opts_chunk$set(
  fig.align = "center",
  dpi = 300
)

set.seed(1)
```

## Problem 1

```{r Data import and Tidying, message = FALSE}
#Importing the data from GH URL like HW5 and mutating/tidying as indicated in the problem 

wp_homicide_data = 
  read_csv("https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(city_state = str_c(city, state, sep = ", "),
         solved = ifelse(disposition == "Closed by arrest", 1, 0)) %>%
  filter(!city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")) %>% 
  mutate(victim_race = ifelse(victim_race != "White", "non-White", "White"), 
         victim_race = fct_relevel(victim_race, "White", "non-White"),
         victim_age = as.numeric(victim_age))
```


```{r Baltimore Model}
# Baltimore-specific glm model saved as an r object

baltimore_model =
  wp_homicide_data %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(solved ~ victim_age + victim_sex + victim_race, family = binomial, data = .)

# Applying broom::tidy to the Baltimore model object, obtaining CIs and exponentiating as it's just a coefficient in original output 

baltimore_model %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate),
         OR_Lower_Bound = exp(estimate - (1.96 * std.error)),
         OR_Upper_Bound = exp(estimate + (1.96 * std.error))) %>% 
  filter(term == "victim_racenon-White") %>% 
  select(OR, OR_Lower_Bound, OR_Upper_Bound, p.value) %>% 
  knitr::kable(digits = 4)
```

From the results of our logisitc model above, we obtain statistically significant results regarding the homicides in Baltimore. 

We see that in Baltimore, the odds of a non-white victim's homicide case being solved is 0.441 times that of a white victim's case being solved. We are 95% confident that the true odds lie between 0.31 and 0.62.

```{r All Cities GLM and plot}
# Running the logistic model for all cities in the dataset by grouping by the citiy and nesting their data, then plotting the OR and CI in descending order

wp_homicide_data %>% 
  group_by(city_state) %>% 
  nest() %>%
  mutate(logit_all = map(data, ~glm(solved ~ victim_age + victim_sex + victim_race, family = binomial, data = .)),
         logit_all = map(logit_all, broom::tidy)) %>%
  select(-data) %>% 
  unnest() %>% 
  filter(term == "victim_racenon-White") %>%
  mutate(OR = exp(estimate),
         OR_Lower_Bound = exp(estimate - (1.96 * std.error)),
         OR_Upper_Bound = exp(estimate + (1.96 * std.error)),
         city_state = fct_reorder(city_state, estimate)) %>%
  select(city_state, OR, OR_Lower_Bound, OR_Upper_Bound) %>% 
  ggplot(aes(x = city_state, y = OR))+
  geom_point(color = "firebrick") + 
  geom_errorbar(aes(ymin = OR_Lower_Bound, ymax = OR_Upper_Bound)) +
  coord_flip() + 
  labs(title = "Adjusted Odds Ratios for Solving Homicides Comparing \n Non-White Victims to White Victims by City", 
       y = "Adjusted Odds Ratio", 
       x = "City, State", 
       caption = "Error Bars represent 95% Confidence Interval of Adjusted Odds Ratio") + 
  theme(axis.text.x = element_text(size = 3),
        plot.title = element_text(hjust = 0.5)) + 
  theme_bw()
```

In the above plot, we see that Tampa, Florida, followed by Birmingham, AL and Durham, NC have the 'highest' adjusted odds ratio, all of which are greater than the null value of 1. This indicates that the odds of a non-white homicide victim's case being solved are greater than a white homicide victim's case being solved. However, they all have wide confidence intervals which include the null value of 1, indicating the relationship isn't significant. 

Addtionally, we see that the 'bottom' five adjusted odds ratios on the plot are Boston, Omaha, Oakland, Pittsburgh, and Cincinnati (in ascending order). This indicates that these cities, with ORs <1, are the least likely to solve a non-white victim's homicide case compared to a white victim's case. The confidence intervals all do not include the null value one, indicating a significant relationship. 

Overall, we see that cities with a large amount of homicides (Baltimore, Chicago) have smaller confidence intervals, while smaller cities with fewwer homicides tend to have large confidence intervals. This is expected, as with more data we can have less variability, our standard errors tend to be smaller.

## Problem 2

Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

```{r Importing and Tidying birthweight data}

bw = read_csv("data/birthweight.csv") %>% 
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace), 
         malform = as.factor(malform), 
         mrace = as.factor(mrace))

# After importing the data, I checked which columns seemed appropriate to be converted to factors from numeric values. Those which where dichotomous or 
# categorical variables and not appropriately continous, I converted using as.factor. 

# Checking for missing data,
# There is no missing data in the data frame when checking each of the columns with the code below: 

# sum(is.na(bw$bwt))
```

Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

```{r Exploratory Plots for Model}
#Exploratory plots to see distribution of birthweight

# No x to plot against, tried this scatter but not much info: bw %>% ggplot(aes(x = 1:nrow(bw), y = bwt)) + geom_point() + theme_bw()

bw %>% 
  ggplot(aes(x = bwt)) +
  geom_histogram(bins = 50) + 
  theme_bw()

bw %>% 
  ggplot(aes(y = bwt)) + 
  geom_boxplot() +
  theme_bw()

# Birthweight is probably fairly normally distributed, with a few outliers, and should be treated as a continous variable in an analysis 

bw %>% 
  ggplot(aes(x = babysex, y = bwt)) + 
  geom_boxplot() +
  theme_bw()

bw %>% 
  ggplot(aes(x = frace, y = bwt)) + 
  geom_boxplot() +
  theme_bw()

bw %>% 
  ggplot(aes(x = mrace, y = bwt)) + 
  geom_boxplot() +
  theme_bw()

# The boxplots for categorical variables tells us a little bit of info, mostly that birthweight varies across all the categories 

# For checking the relationships with continuous variables, I'll run a function to determine the correlation coefficients 



```

